---
title: "retweet network"
output: html_notebook
---


# install packages and run the packages
```{r}
install.packages("networkD3") # it is for interactive network visualization
install.packages("twitteR") 
install.packages("igraph") # it is for network analysis
install.packages("stringer")
install.packages("dplyr")
install.packages("qdap")

library(twitteR)
library(dplyr)
library(qdap)
library(networkD3)
library(igraph)
library(stringr) 

```

#we will now extracting data and collect tweets

```{r}

api_key <- "T8CKcDTkHJJIlSJkKWCIAJqeF"
api_secret <- "CK4wWEPHd2tliA5ghVY3eBwlCEXE7m5FZsie0gitfN4dSdH9VD"
access_token <- "844615642993082368-RJIO1uLbjPeribYc3oUEfvy9cA2C6dS"
access_token_secret <- "JVvpbJ5dARihNkcWLun4uCh6yTqOY4MZZrOibk6JzD9p1"
setup_twitter_oauth(api_key, api_secret, access_token, access_token_secret)

alltweets <- twListToDF(searchTwitter("#stephencurry", n=500, retryOnRateLimit=120))
```
#Network analysis and visualization is computationally intensive. We will use only the first 200 tweets for demo.
```{r}
alltweets<-alltweets[1:200,]
#split the data into two sets; one for retweet network and the other for mention network.
#create an edge-list for retweet network
sp = split(alltweets, alltweets$isRetweet)
rt = mutate(sp[['TRUE']], sender = substr(text, 5, regexpr(':', text) - 1)) # # Extract the retweets and pull the original author's screenname
el = as.data.frame(cbind(sender = tolower(rt$sender), receiver = tolower(rt$screenName))) 
el = count(el, sender, receiver) #adjust retweets to create an edgelist for network
el[1:5,] #show the first 5 edges in the edgelist

```
# Twitter’s API doesn’t tell us where a retweeter saw the tweet that they retweeted; an edge always goes from the original author of the tweet to the retweeter, so we can’t follow the diffusion of a tweet. But, we can get a sense of who is being retweeted, and we see a core of individuals engaging in a conversation at the center of the graph. Nodes are sized to their total degree (retweeting and being retweeted), and edge-width is proportional to the number of retweets between that pair. Labeled nodes are those that were retweeted at least once.

```{r}
# Based on the edge-list, create a retweet network.
rt_graph <- graph_from_data_frame(d=el, directed=T)
#Visualize the retweet network.
glay = layout.fruchterman.reingold(rt_graph) 
plot(rt_graph)


```

# we will now to improve the visualzation
```{r}
glay = layout.fruchterman.reingold(rt_graph)
par(bg="gray15", mar=c(1,1,1,1))
plot(rt_graph, layout=glay,
     vertex.color="gray25",
     vertex.size=(degree(rt_graph, mode = "in")), #sized by in-degree centrality
     vertex.label = NA,
     edge.arrow.size=0.8,
     edge.arrow.width=0.5,
     edge.width=edge_attr(rt_graph)$n/10, #sized by edge weight
     edge.color=hsv(h=.95, s=1, v=.7, alpha=0.5))
title("Retweet Network", cex.main=1, col.main="gray95")


```

#The above network visualization does not show vertex label. Let’s add a few lines to make the graph more informative. igraph is a very versatile by allowing a high degree of customization for visualization.
```{r}
glay = layout.fruchterman.reingold(rt_graph)
par(bg="gray15", mar=c(1,1,1,1))
plot(rt_graph, layout=glay,
     vertex.color="gray25",
     vertex.size=(degree(rt_graph, mode = "in")), #sized by in-degree centrality
     vertex.label.family="sans",
     vertex.shape="circle",  #can also try "square", "rectangle", etc. More in igraph manual
     vertex.label.color=hsv(h=0, s=0, v=.95, alpha=0.5),
     vertex.label.cex=(degree(rt_graph, mode = "in"))/300, #sized by in-degree centrality
     edge.arrow.size=0.8,
     edge.arrow.width=0.5,
     edge.width=edge_attr(rt_graph)$n/10, #sized by edge weight
     edge.color=hsv(h=.95, s=1, v=.7, alpha=0.5))
title("Retweet Network", cex.main=1, col.main="gray95")


```


```{r}
wc <- cluster_walktrap(rt_graph)
members <- membership(wc)
d3_rt <- igraph_to_networkD3(rt_graph, group = members)

forceNetwork(Links = d3_rt$links, Nodes = d3_rt$nodes, 
             Source = 'source', Target = 'target', 
             NodeID = 'name', Group = 'group')
```


